Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-11-02 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
reviewed sections 3, 4, 5 and 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\section{Design and Validation of a Solar photovoltaic system}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this work, were evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.

@@

Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.  Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis; 
and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis. However, only paid version of those softwares have all the features, and they run only at Windows operational systems. RETScreen and HOMER have a free web-based version but with limited resources.

@@

\subsection{Paper Proposal x Reference Tools}
Considering the focus of this paper, only HOMER remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
After that, the potential solution is analyzed in another tool to validate or even optimize the solution. Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools. The comparative between the HOMER Pro and the automated verification tool is presented at the Section \ref{sec:results}.

\section{Component models for stand-alone PV system }
%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system (Source: \cite{Hansen})}
\label{fig:blockdiagram}
\end{figure}

@@

\subsection{PV generator model}
%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
%In the present modeling, the focus is only on cell/module/array.
%
The basic element of a PV system is the PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
package called panel or module.

@@

The performance of photovoltaic systems, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model, as shown by \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}.

\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{ 1-diode equivalent PV cell/panel circuit model (Source: \cite{Cubas})}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

@@

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Summary of the controller process (Source: \cite{Hansen})}
\label{table:controller}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c | c | c }
\hline
\hline
Step  & Constraint & Command\\
\hline
\hline
(1) & \makecell{If $V > V_{max \textunderscore off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
\hline
(2) & \makecell{If command (1) is \\done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array \\to the system}\\
\hline
(3) & \makecell{If $V < V_{min \textunderscore off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
\hline
(4) & \makecell{If command (3) is \\ done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load \\to the system}\\
\hline
\hline
\end{tabular}
\end{table}

@@

\section{Related work }
%The CBMC, it is notable its prominence through international awards received in competitions. 
%In the works r
Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly), without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.

@@

\section{Conclusions and Future Work}
%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field. 
%
%The framework presented here establishes the automated verification and the project sizing check. 
It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results. The framework was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems. That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system. 
Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs. This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

@@

>>>>

\section{Design and Validation of a Solar photovoltaic system}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
Here we evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.

@@

Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER Pro and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis; 
additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis. However, only paid version of those tools have all the features \textcolor{red}{which features?}, and they run only on Windows operating system. RETScreen and HOMER have a free web-based version, but they have limited resources.

@@

%-------------------------------------------------------------------
\subsection{Paper Proposal x Reference Tools}
%-------------------------------------------------------------------

Considering the focus of this paper, only HOMER remains for our comparative evaluation. All tools need some parameters inherently from manufacturer's catalog \textcolor{red}{is this the correct term? to size the system}.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
After that, the potential solution is analyzed in another tool to validate or even optimize the solution. Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than other state-of-the-art tools \textcolor{red}{cite them here...}. The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.

%-------------------------------------------------------------------
\section{Component models for stand-alone PV system }
%-------------------------------------------------------------------

%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram} \textcolor{red}{you should explain each element of the figure}. The modular structure facilitates the modeling of the other system structures and replacement of elements such as a DC load instead of an AC load.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system~\cite{Hansen}}.
\label{fig:blockdiagram}
\end{figure}

@@

%-------------------------------------------------------------------
\subsection{PV generator model}
%-------------------------------------------------------------------

%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
%In the present modeling, the focus is only on cell/module/array.
%
The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
package called panel or module.

@@

The performance of photovoltaic systems, %that is, the output current/voltage curve ($I-V$ curve), 
is usually studied using an equivalent circuit model, as described in the available literature \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. 
%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}.

\begin{figure}[h]
\includegraphics[width=0.20\textwidth]{equivckt1D}
\centering
\caption{ 1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

@@

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Summary of the controller process~\cite{Hansen}}
\label{table:controller}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c | c | c }
\hline
\hline
Step  & Constraint & Command\\
\hline
\hline
(1) & \makecell{If $V > V_{max \textunderscore off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
\hline
(2) & \makecell{If command (1) is \\done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array \\to the system}\\
\hline
(3) & \makecell{If $V < V_{min \textunderscore off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
\hline
(4) & \makecell{If command (3) is \\ done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load \\to the system}\\
\hline
\hline
\end{tabular}
\end{table}

@@

%-------------------------------------
\section{Related work }
%-------------------------------------

\textcolor{red}{This section needs more work. You should describe here studies related to the design, verification or validation of PV systems and not about software model checkers!}

%The CBMC, it is notable its prominence through international awards received in competitions. 
%In the works r
Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly), without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.

@@

%-------------------------------------
\section{Conclusions and Future Work}
%-------------------------------------

%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field. 
%
%The framework presented here establishes the automated verification and the project sizing check. 
It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results. The framework was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems. That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system. 
Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs. This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

@@

\textcolor{red}{You should revise all references according to the journal guideline.}
